Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
removed a bunch of outdated/unnecessary stuff
re-organized with respect to the placement of color correction discussion

%In light of the \PLANCK~HFI data, it is possible to revisit the best-fit 
%global parameters of the two-component emission model. To derive the 
%\{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} that best represent the \PLANCK~HFI
%maps, we employed a correlation slope analysis (see Figure XX). Specifically,
%we correlated the observed \PLANCK~data against the appropriate FDS99 
%prediction for each HFI band from 143-857 GHz. We omitted 100 GHz from 
%consideration due to the sensitivity of the 100 GHz trend to our ad hoc
%low order corrections (see Figure \ref{fig:harm}). All comparisons between
%\PLANCK~and the FDS99 predictions were made after smoothing both to 
%$1^{\circ}$, subtracting the SMICA CMB model, and ignoring SMICA inpainted 
%pixels. For 100-857 GHz, the linearity between the FDS and \PLANCK~is
%excellent.

%also emphasize that FDS99 predictions are broadband, not monochromatic
% (i think i can borrow a sentence about this from the absolute zero point 
% section above)

%However, the slopes at low frequencies are not precisely unity, as would
%be expected if the global two-component parameters derived from FIRAS by
%FDS99 were also the best-fitting global parameters with respect to the 
%\PLANCK~data set.

%We then derive \{$\beta_1$, $\beta_2$, $f_1$, $q_1/q_2$\} as constrained by 
%the correlation slopes and their uncertainties given in Table QQ by 
%taking $T_2$=$16.2$K and running Markov chains to sample the posterior:

%Figure ZZ shows a corner plot of the 150,000 samples. Clearly, there are
%strong covariances, but even so several conclusions are clear: (1) a lower 
%value of $q_1/q_2$ is favored by the \PLANCK~data than by the FIRAS data (2) 
%the best-fit emissivity power law index of the hot dust component ($\beta_2$) 
%is effectively identical to that found by FDS99 to within uncertainties and 
%(3)
%a somewhat lower $\beta_1$ is favored by \PLANCK~than by FIRAS, meaning the
%\PLANCK-based SED is shallower toward the millimeter. Because $f_1$ is so 
%strongly covariant with $\beta_1$, the difference of $f_1$ between the 
%\PLANCK~and FIRAS best fits is not particularly significant.

% actually quantitatively assess, for a typical temperature (and frequency?)
% how the new f_1 value basically balances out the change in beta_1 ???

%The MCMC fitting procedure described in $\S$\ref{sec:fitting} is performed
%separately for both model 1 (FIRAS+\verb|i100|) and model 2 
%(\PLANCK+\verb|i100|), each defined by their respective global parameters 
%listed in Table \ref{tab:global}.

% does this statement accidentally give the impression that I do separate 
% MCMC fits, one in which i fit Planck/IRAS **data** and one in which
% i fit FIRAS/IRAS data ????

% multi-panel figure showing more scatterplots of Planck vs. FDS predictions

%\subsection{Hierarchical Approach?}

\subsection{Color Correction}
\label{sec:bpcorr}
The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
$\nu$. In practice, however, we wish to constrain our model using measurements 
in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
The \PLANCK~data products quote flux density per solid angle in MJy/sr under 
the `IRAS convention'. More precisely, each value reported in the \PLANCK~maps 
gives the amplitude of a power-law spectrum with $\alpha$=$-1$, evaluated at 
the nominal band center frequency, such that this spectrum integrated against 
the transmission reproduces the bolometer-measured power. Because our model 
spectra do not conform to the $\alpha$=$-1$ convention, we have computed color 
correction factors to account for the MBB($T$, $\beta$) spectral shape and the 
transmission as a function of frequency:

@@

\subsection{Predicting the Observed SED}
With the formalism established in $\S$\ref{sec:modeling} and 
$\S$\ref{sec:bpcorr}, we can mathematically state the model we will use during 
MCMC sampling to predict the observed SED, which we will denote by 
\{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:

@@

>>>>

\section{Predicting the Observed SED}
\label{sec:bpcorr}

The thermal dust emission model of $\S$\ref{sec:modeling} predicts the 
flux density per solid angle $M_{\nu}$ in e.g. MJy/sr for any single frequency 
$\nu$. In practice, however, we wish to constrain our model using measurements 
in the broad \verb|i100|/\PLANCK~bandpasses, each with $\Delta\nu/\nu\sim0.3$. 
Both the \PLANCK~data and DIRBE data products quote flux density per solid 
angle in MJy/sr under the `IRAS convention'. More precisely, each value 
reported in the \PLANCK~maps gives the amplitude of a power-law spectrum 
with $\alpha$=$-1$, evaluated at the nominal band center frequency, such that 
this spectrum integrated against the transmission reproduces the 
bolometer-measured power. Because our model spectra do not conform to the 
$\alpha$=$-1$ convention, we have computed color correction factors to account 
for the MBB($T$, $\beta$) spectral shape and the transmission as a function of 
frequency:

@@

With these color corrections and the  formalism established in 
$\S$\ref{sec:modeling} in hand, we can mathematically state the model we will 
use e.g. during MCMC sampling to predict the observed SED, which we will 
denote by \{$\tilde{I}_{\nu_i}$\}. The predicted observations are given by:

@@

%All comparisons between %\PLANCK~and the FDS99 predictions were made after 
%smoothing both to $1^{\circ}$, subtracting the SMICA CMB model, and ignoring 
%SMICA inpainted pixels. For 100-857 GHz, the linearity between the FDS and 
%\PLANCK~is excellent.
